\Title

### 2022-09-27 Grimaldi-etal-BiolCybernetics.tex
Introduction: 1.1

% 1.1.2 b

\subsection{What can neuroscience bring to computer vision?}% and the Hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------

>>>>

% 1.1.2 b
Challenges are numerous in
that case and we should
put forward two major ones:
rapidity and energy budget.
First, most existing solutions are
being built incrementally from
low-definition images such as
Le Net for MN is T (Le Cun, 98),
to high definition images, such as
V94 on Imagen et (V9 416).
This comes at a cost and notably
that the computation time increases
with image size. This has been tampered
by the increase of computational power
available, notably with the parallel
processing implemented in GPU cards.
However, transitioning from images
to videos, and then to multiple cameras
involves a change of scale in the
amount of data processed. It
raises also a question which is often
of little importance in image
categorization. Indeed, in the setting
of autonomous driving, an important
task is to respond as fast as possible
be a eventual collision, for instance as
a pedestrian crosses the street. As such,
future systems should always be able
to give a response at any time, instead
of having to wait until the pipeline
delivers the correct response. This
online processing is also a hallmark
of processing in biological systems.
This could be a first important
contribution if we could translate
these principles into future automated
processes.

second, a major constraint on
futur systems is energy budget.
As we saw, a fait computation
time was kept for high-dimension
images, but this come at the cost
of a higher energy consumption.
Also, the need he solve increasingly
more complex tasks necessitated the
construction of increasingly more
complex and deepen architectures.
As en exaupte the top performing
net on the Imagent challenge is
using billions of parameters which
tipycally cost 1Wh to train and
approximately 1Wh per inference
of a single image. Less greedy
solutions have emerged such
as Mobile Net, yet these solutions
are yet not pit to be used
in practice in autonomous
Lars, as the added consumption
would be approximately Bow
that is, 200 to of the energy
of an electric can in standaro
conditions.

Neuroscience could bring
breakthrough answers to these
two intertwined problems-Indeed
the human brain has the remarkable
property of being mostly autonomous
in it a learning, to be able to act
and respond at any time, and get to
consume en reasonable amount of energy,
estimated to 5W at rest. This system
is the result of million of years of natural
selection, get a striking property of
biological neural networks compared
to an artificial one is their respective
representation. CNN s for instance
represent the information passing from
one lage to the other as tensons representing
visual information in a dense manner on
the visual topography, while representing
different properties in different channels.
On the other side, information in avait
majority of biological neural networks
is represented as spikes, that is, as
prototypical all-or-none events whose
only parameters are their timing and
the address of the neuron that emitted
that spite. Why spikes ? It is not
yet known the reason why most systems
evolved to use that representation, but
one major advantage sans to be a
form of efficiency. In the human brain,
each of the about to trillion nerve cells
emit on average 1 spike per second,
but with a high variability and up to
300 spikes per second. There has been
numerous attempts to build artificial
spiking neural networks, and
notabley to have the same performance
en that observed in classical cans, yet
with a lower energy budget. Yet, un
such SNN has yet surpassed state-of
the art performances. Here, we will attempt
to focus on a neurobiologically inspired
property of spiking neurons to advance
in that endeavour.

\subsection{What can neuroscience bring to computer vision?}% and the Hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------
% 1.2.a
